Capturing subdiffusive solute dynamics and predicting long timescale selectivity in nanoscale pores with time series modeling

### 2020-01-08 Ben_Manuscripts/stochastic_transport/Draft.tex
Consolidating

\documentclass{article}

@@

  Solutes in this system very clearly exhibit subdiffusive behavior, a type of
  anomalous diffusion. During an anomalous diffusion process, the mean squared 
  displacement (MSD) does not grow linearly with time, but instead it follows 
  a power law of the form:
  %MRS6: do you need the subscript for $\alpha$? makes it harder to read. 
  \begin{equation} 
  \langle z^2(t) \rangle = K_{\alpha_d}t^{\alpha_d}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha_d$ is the anomalous exponent and $K_{\alpha_d}$ is the generalized 
  diffusion coefficient. We only calculate MSD with respect to the solutes' center of
  mass $z$-coordinate, which is oriented along the pore axis. A value of $\alpha_d < 1$
  indicates a subdiffusive process, while values of $\alpha_d = 1$ and $\alpha_d > 1$ 
  are characteristic of Brownian and superdiffusive motion respectively.

@@

  We chose to analyze just the time-averaged MSD because, compared to the ensemble
  average, it is a more statistically robust measure of the average distance a 
  solute travels over time. 
  % MRS6: does it correspond properly to the physical situation of entry into the 
  % pore of new particles at each unit time?
  % BJC6: no, but neither does ensemble
  Although theoretically possible, we do not use the ensemble averaged MSD to 
  calculate $\alpha_d$ because we can extract the same parameter with higher 
  precision using the dwell time distributions as described below.

%  Only the \textit{ensemble} averaged MSD will reproduce the form of 
%  Equation~\ref{eqn:msd_form} in all cases.
%  
%  We analyzed the time-averaged MSD of the simulated trajectories by measuring
%  all possible displacements over time lag $\tau$:
%  \begin{equation}
%  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
%  \end{equation}
%  where T is the length of the trajectory. Note that only the \textit{ensemble} MSD
%  will reproduce the form of Equation~\ref{eqn:msd_form} in all cases. The ensemble
%  MSD is given by:
%  \begin{equation}
%  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
%  \label{eqn:ensemble_msd}
%  \end{equation} 
%  In a pure CTRW, for example, the power law distribution of trapping times leads to
%  weak ergodicity breaking. In this case, the time-averaged MSD is linear while the ensemble averaged
%  MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With power
%  law trapping behavior, the time between hops diverges so there is no characteristic
%  measurement time scale of solute motion. In fact, as measurement time increases, the 
%  average MSD of a CTRW tends to decrease, a phenomenon called aging, because trajectories 
%  with trapping times on the order of the measurement time get incorporated into the 
%  calculation.~\cite{bel_weak_2005} We chose to analyze just the time-averaged MSD 
%  because, compared to the ensemble average, it is a more statistically robust measure
%  of the average distance a solute travels over time. 
%  %MRS6: does it correspond properly to the physical situation of entry into the pore of new particles at each unit time?
%  Although theoretically possible, we do
%  not use the MSD to calculate $\alpha_d$ because we can extract the same parameter 
%  with higher precision using the dwell time distributions as described below.

@@

  \textit{Dwell time distributions:} For subdiffusive transport, the distribution 
  of dwell times is expected to fit a power law distribution 
  proportional to $t^{-1-\alpha_d}$.~\cite{meroz_toolbox_2015}
  Because we are limited to taking measurements at discrete intervals dictated by the output 
  frequency of our simulation trajectories, we fit the empirical dwell times
  to a discrete power law distribution whose maximum likelihood $\alpha_d$ 
  parameter we calculated by maximizing the likelihood function: 
  \begin{equation}
	\mathcal{L}(\beta) = -n\ln \zeta(\beta, t_{min}) -
	\beta\sum_{i=1}^{n} \ln t_i 
  \label{eqn:powerlaw_likelihood}
  \end{equation}
  where $\beta = 1 + \alpha_d$, $t_i$ are collected dwell time data points,
  $n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
  where $t_{min}$ is the smallest measured value of	$t$.~\cite{clauset_power-law_2009}

  In practical applications, the heavy tail of power law distributions can result in 
  arbitrarily long dwell times that are never observed in MD simulations. We cannot
  observe dwell times longer than the length of a single trajectory. 
  In order to directly compare our anomalous diffusion model to finite-length MD 
  trajectories we need to bound the dwell time distribution. We do this by adding 
  an exponential cut-off to the power law so the dwell time distribution is 
  now proportional to $t^{-1 - \alpha_d}e^{-\lambda t}$.
  %MRS6: are there papers to cite that this is a standard way to cut them off (i.e. rather than truncate, etc).
  % of the form:
%  \begin{equation}  %BJC3: maybe make this equation in line? Else move regular power law to its own equation
%    p(t) \propto t^{-1 - \alpha}e^{-\lambda t}
%  \label{eqn:powerlaw_cutoff}
%  \end{equation}
  We determine MLEs of $\alpha_d$ and $\lambda$ by maximizing the likelihood function:~\cite{clauset_power-law_2009}
  \begin{equation}
    \mathcal{L}(\alpha_d, \lambda) = n(1 - \alpha_d)\ln\lambda - n\ln\Gamma(1 - \alpha_d, t_{min}\lambda) - \alpha_d\sum_{i=1}^{n}\ln t_i - \lambda\sum_{i=1}^n t_i
  \label{eqn:powerlaw_cutoff_likelihood}
  \end{equation}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{1mode_AD_hops.pdf}
  \caption{}\label{fig:1mode_AD_hops}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{1mode_AD_dwells.pdf}
  \caption{}\label{fig:1mode_AD_dwells}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{hurst_barchart.pdf}
  \caption{}\label{fig:hurst_barchart}
  \end{subfigure}
  \caption{The parameters of the 1 mode model reveal differences in solute dynamics.
  (a) We parameterized Gaussian, $\mathcal{N}(\sigma)$, and L\'evy stable, 
  $L(\sigma, \alpha_h)$, distributions to describe solute hop lengths. We assume the 
  mean ($\mu$) to be zero for these distributions and there to be no skewness ($\beta = 0$)
  in the L\'evy stable disributions. High values of $\sigma$ and lower values of $\alpha_h$
  result in larger hops. (b) We parameterized a pure power law, $P(\alpha_d)$, and a 
  truncated power law, $P_T(\alpha_d, \lambda)$, distribution to describe solute dwell
  times. Lower values of $\alpha_d$ lead to heavier power law tails and higher values of 
  $\lambda$ truncate the distibution at lower dwell times. (c) Finally, we parameterized the
  hop autocorrelation function, $\gamma(H)$, to describe the degree of correlation between
  hops. Higher values of $H$ display closer to Brownian behavior.}\label{fig:1mode_parameters}
  \end{figure}

  \begin{figure}
  \centering
  \begin{subfigure}{0.475\textwidth}
  \includegraphics[width=\textwidth]{2mode_AD_hops.pdf}
  \caption{}\label{fig:2mode_AD_hops}
  \end{subfigure}
  \begin{subfigure}{0.475\textwidth}
  \includegraphics[width=\textwidth]{2mode_AD_dwells.pdf}
  \caption{}\label{fig:2mode_AD_dwells}
  \end{subfigure}
  \caption{
  %MRS6: shouldnt the values be positive below the axis as well (if that can be done) I guess they are for b, but not for A.
  %BJC6: yes, oversight, thanks.
  The two mode model parameterizes solute behavior in the pore and tails separately.
  We consider solutes to be within the pore region if they are 0.75 nm from a given pore
  center, otherwise they are in the tails. (a) Generally, movement is much more restricted
  in the tail region shown by lower $\sigma$ values (smaller hops) for the normal and L\'evy stable 
  distributions. Values of $\alpha$ are significantly lower for urea and acetic acid meaning 
  there is a larger probability that they will take large hops. (b) Dwell times are longer in 
  the tails. Lower values of $\alpha_d$ correspond to power laws with heavier tails and 
  thus higher probabilities of long dwell times. There is no easily discernable trend in
  $\lambda$ of the truncated power law distribution. Note that we used the same Hurst parameter
  for both modes (shown in Figure~\ref{fig:hurst_barchart}) due to a low number of 
  sufficiently long sequences of hops in each mode.}
  \label{fig:2mode_parameters}
  \end{figure}

@@

  The model parameters for the 1 and 2 mode models tell stories about each solute's
  behavior that help explain the difference between the MSDs of different solutes. 
  %BJC6: need to double check this after alpha_h c parameter simulations are re-done
  Higher values of $\sigma$ and lower values of $\alpha_h$ indicate larger average 
  hop length magnitudes by increasing the hop length distribution's width and tail 
  density respectively. Higher values of $\alpha_d$ indicate a lower probability of 
  long dwell times. Higher values of $\lambda$ truncate the power law distribution 
  earlier preventing extremely long dwell times. Values of $H$ closer to the Brownian
  limit of 0.5 indicate a lower degree of negative correlation between hops. All 
  of these model parameters contribute to 
  %MRS6: increase in the MSD compared to what, be specific?
  %BJC6: made more specific
  an overall increase in the predicted MSD and can be correlated to physical behavior 
  that explains differences in the MD MSDs.

  Turning first to the parameters of the 1 mode model, we can begin to break down the
  trends in solute MSDs. The parameters belonging to ethylene glycol and methanol are
  relatively similar which is consistent with their similar MD MSDs. Methanol 
  tends to stay trapped for less time and takes larger hops but the most substantial
  difference is with respect to their Hurst parameters. In fact, methanol has the lowest
  $H$ of all the solutes studied. It is possible that we have underestimated $H$ since 
  it appears that our model under-predicts the methanol MSD curve relative
  to other solutes. However, it remains plausible that methanol does have a low $H$ 
  value because it spends the majority of its time outside the pore region where collisions
  with tails are frequent. Urea has the third highest MSD which is primarily a consequence of
  more frequent and longer dwell times, indicated by lower values of $\alpha_d$ and 
  $\lambda$. Urea's hop lengths ($\sigma$) and correlation ($H$) are comparable to ethylene
  glycol and methanol. Acetic acid has the smallest MSD among the solutes studied due 
  to longer periods of entrapment and shorter hops. Its trapping behavior is parameterized
  by an $\alpha_d$ value significantly lower than other solutes, but an intermediate 
  $\lambda$ value, suggesting it experiences many medium length periods of entrapment. 
  Its hops are smaller but are slightly compensated by a heavier tailed distribution 
  (lower $\alpha_h$) than the other solutes.

  We can use the 2 mode model to gain an even deeper understanding of solute behavior
  in the pore versus in the tails. It is clear that solutes are significantly slowed 
  while they are in the tail region where long dwell times are more probable
  (smaller $\alpha_d$) and hops are smaller (smaller $\sigma$). Each solute spends 
  a different amount of time in the tails (see Figure~\ref{fig:AD_mode_occupation}). 
  Urea and acetic acid spend slightly more than half of their time in the tails 
  (56\% and 62\% of their time respectively) while ethylene glycol spends about 
  44\% of its time in the tails. Urea and acetic acid's compact and flat structure 
  allows it to more easily partition into the tails while ethylene glycol prefers
  the pore region due to its two hydrophilic hydroxyl groups. Meanwhile methanol 
  spends 91\% of its time in the tails likely due to its small size.  
  The value of $\alpha_h$ for urea and acetic acid in the tails is 1.50, meaning its hop distribution
  is heavy tailed relative to ethylene glycol and methanol whose $\alpha_h$ values are
  more consistent with a Gaussian distribution ($\alpha$=2). Acetic acid and urea are
  structurally similar molecules, both planar with two heavy atoms attached to a 
  carbonyl group. Their small size and rigid shape may allow them to occasionally slip
  through gaps in the tails. Meanwhile, methanol is small enough that it does not need
  to make larger jumps to escape traps.

@@

%  The parameters of the 1 mode model indicate some diversity in solute behavior. The value
%  of $\alpha_d$ for pure and truncated power law fits to the dwell time distributions of 
%  urea, ethylene glycol and methanol are similar. The value of $\alpha_d$ for acetic
%  acid is significantly lower than the rest of the solutes meaning it stays trapped 
%  for long periods of time more frequently. The value of $\lambda$ is largest for
%  methanol indicating that its longest dwell time is shorter than the longest dwell
%  times of all other solutes. When hops are fit to a Gaussian, it is clear that acetic
%  acid takes the smallest hops while methanol takes the largest. If we fit hops to a
%  L\'{e}vy stable distribution, we observe a similar trend in $\sigma$ values, but 
%  with varying weights on the distribution's tails. Acetic acid has the heaviest
%  tails (lowest $\alpha_h$), meaning it is more likely to take large hops, while 
%  ethylene glycol stays close to a Gaussian distribution (i.e. $\alpha_h$ near 2).
%  The Hurst parameters indicate a moderate degree of anti-correlation between hops. 
%  Surprisingly, methanol takes the most anti-correlated hops (lowest $H$). This is
%  likely because methanol spends the largest fraction of its time within the pores. 
%  It can still make large hops thanks to its small size, but tends to bounce around
%  the tails.

%  BJC4: urea and ethylene glycol only
%  The parameters of the 1 mode model are similar between urea and ethylene glycol which 
%  is not surprising considering their similar MD MSDs. Dwell times by 
%  ethylene glycol are shorter as shown by its larger $\alpha_d$ and $\lambda$ values. Both
%  solutes make similarly sized hops with hop distributions that are relatively close 
%  to Gaussian (i.e. $\alpha_h$ near 2) when fit to a L\'evy stable distribution. Finally,
%  both solutes exhibit a similar degree of correlation between hops with ethylene glycol
%  exhibiting motion closer to Brownian.

%  The difference in parameters of each mode of the 2 mode sFBM model offer additional
%  mechanistic insight which the 1 mode model lacks. It is clear that solutes are 
%  significantly slowed while they are in the tail region (mode 2) where long dwell times
%  are more probable and hops are smaller (smaller $\alpha_d$). 
% BJC: I'm not sure how valid it is to analyze lambda because it is dependent on alpha. There is some counterbalancing going on.  
% The values of $\lambda$, however, do not 
% appear to be directly correlated to mode. For example, $\lambda$ for ethylene glycol is
% lower in the pores, meaning its longest dwell times in the pores are longer than its
% longest dwell times in the tails. This may be a consequence of    
%  Interestingly, $\alpha_h$ for urea and acetic acid in mode 2 is 1.50 meaning its 
%  hop distribution is heavy tailed relative to ethylene glycol and methanol whose 
%  $\alpha_h$ values are more consistent with a Gaussian distribution. Acetic acid and
%  urea are structurally similar molecules, both planar with two heavy atoms attached to
%  a carbonyl group. Their small size and rigid shape may allow them to slip through 
%  gaps in the tails. Meanwhile, methanol is small enough that it does not need to make 
%  larger jumps to escape traps.

%  BJC4: Urea and ethlyene glycol only
%  The parameters of the 2 mode model are again similar between urea and ethylene glycol, 
%  but the difference between parameters of each mode offer more detailed mechanistic
%  insight than the 1 mode model. It is clear that solutes are significantly slowed while
%  they are in the tail region where long dwell times are more probable (lower $\alpha_d$)
%  and hops are smaller (smaller $\sigma$).  
%  Interestingly, $\alpha_h$ for urea in mode 2 is 1.50 meaning its hop distribution is
%  heavy tailed relative to ethylene glycol which has an $\alpha_d$ more consistent 
%  with a Gaussian distribution. Although urea's $\sigma$ parameter is much smaller in 
%  the tails, it still has an appreciable probability of making large hops. This could 
%  be a consequence of urea's relatively small size and rigid shape compared to ethylene glycol.
  %Ethylene glycol is a linear chain that can
  %easily become entangled among the alkane tails while urea is planar with its four
  %heavy atoms bonded to a single central atom.

@@

  To understand the behavior of the MSDDM, we studied the $\beta$ parameter derived 
  from variations on each model, visualized in Figure~\ref{fig:beta_parameters}. First, 
  we removed anti-correlation between hops in the sFBMcut trajectory (set $H$=0.5). 
  The $\beta$ parameter drops to values similar to the MSDDM. When we remove anti-correlation
  \textit{and} dwell times between hops (set dwell times equal to 1), effectively simulating 
  Brownian motion, we observe similar $\beta$ parameters. These two variations imply that,
  in the AD models, the $\beta$ parameter is only a function of $H$ and not dependent on
  dwell times ($\alpha_d$, $\lambda$) or hop lengths ($\sigma$). The MSDDM is fundamentally similar to 
  the AD model in that one makes correlated draws from a hop distribution. Therefore,
  we should expect the $\beta$ value of the MSDDM to be larger than that of Brownian 
  motion.
  %Although the dwell times are
  %insignificant compared to the AD model (compare Figures~\ref{fig:ad_eyetest} and
  %\ref{fig:msddm_eyetest} for example), we have just shown

>>>>

\documentclass[12pt]{article}

@@

  Solutes in this system very clearly exhibit subdiffusive behavior, a type of
  anomalous diffusion. During an anomalous diffusion process, the mean squared 
  displacement (MSD) does not grow linearly with time, but instead it follows 
  a power law of the form:
  %MRS6: do you need the subscript for $\alpha$? makes it harder to read. 
  \begin{equation} 
  \langle z^2(t) \rangle = K_{\alpha}t^{\alpha}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha$ is the anomalous exponent and $K_{\alpha}$ is the generalized 
  diffusion coefficient. We only calculate MSD with respect to the solutes' center of
  mass $z$-coordinate, which is oriented along the pore axis. A value of $\alpha < 1$
  indicates a subdiffusive process, while values of $\alpha = 1$ and $\alpha > 1$ 
  are characteristic of Brownian and superdiffusive motion respectively.

@@

  We chose to analyze just the time-averaged MSD because, compared to the ensemble
  average, it is a more statistically robust measure of the average distance a 
  solute travels over time. 
  % MRS6: does it correspond properly to the physical situation of entry into the 
  % pore of new particles at each unit time?
  % BJC6: no, but neither does ensemble
  Although theoretically possible, we do not use the ensemble averaged MSD to 
  calculate $\alpha$ because we can extract the same parameter with higher 
  precision using the dwell time distributions as described below.

%  Only the \textit{ensemble} averaged MSD will reproduce the form of 
%  Equation~\ref{eqn:msd_form} in all cases.
%  
%  We analyzed the time-averaged MSD of the simulated trajectories by measuring
%  all possible displacements over time lag $\tau$:
%  \begin{equation}
%  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
%  \end{equation}
%  where T is the length of the trajectory. Note that only the \textit{ensemble} MSD
%  will reproduce the form of Equation~\ref{eqn:msd_form} in all cases. The ensemble
%  MSD is given by:
%  \begin{equation}
%  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
%  \label{eqn:ensemble_msd}
%  \end{equation} 
%  In a pure CTRW, for example, the power law distribution of trapping times leads to
%  weak ergodicity breaking. In this case, the time-averaged MSD is linear while the ensemble averaged
%  MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With power
%  law trapping behavior, the time between hops diverges so there is no characteristic
%  measurement time scale of solute motion. In fact, as measurement time increases, the 
%  average MSD of a CTRW tends to decrease, a phenomenon called aging, because trajectories 
%  with trapping times on the order of the measurement time get incorporated into the 
%  calculation.~\cite{bel_weak_2005} We chose to analyze just the time-averaged MSD 
%  because, compared to the ensemble average, it is a more statistically robust measure
%  of the average distance a solute travels over time. 
%  %MRS6: does it correspond properly to the physical situation of entry into the pore of new particles at each unit time?
%  Although theoretically possible, we do
%  not use the MSD to calculate $\alpha$ because we can extract the same parameter 
%  with higher precision using the dwell time distributions as described below.

@@

  \textit{Dwell time distributions:} For subdiffusive transport, the distribution 
  of dwell times is expected to fit a power law distribution 
  proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
  Because we are limited to taking measurements at discrete intervals dictated by the output 
  frequency of our simulation trajectories, we fit the empirical dwell times
  to a discrete power law distribution whose maximum likelihood $\alpha$ 
  parameter we calculated by maximizing the likelihood function: 
  \begin{equation}
	\mathcal{L}(\beta) = -n\ln \zeta(\beta, t_{min}) -
	\beta\sum_{i=1}^{n} \ln t_i 
  \label{eqn:powerlaw_likelihood}
  \end{equation}
  where $\beta = 1 + \alpha$, $t_i$ are collected dwell time data points,
  $n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
  where $t_{min}$ is the smallest measured value of	$t$.~\cite{clauset_power-law_2009}

  In practical applications, the heavy tail of power law distributions can result in 
  arbitrarily long dwell times that are never observed in MD simulations. We cannot
  observe dwell times longer than the length of a single trajectory. 
  In order to directly compare our anomalous diffusion model to finite-length MD 
  trajectories we need to bound the dwell time distribution. We do this by adding 
  an exponential cut-off to the power law so the dwell time distribution is 
  now proportional to $t^{-1 - \alpha}e^{-\lambda t}$.
  %MRS6: are there papers to cite that this is a standard way to cut them off (i.e. rather than truncate, etc).
  % of the form:
%  \begin{equation}  %BJC3: maybe make this equation in line? Else move regular power law to its own equation
%    p(t) \propto t^{-1 - \alpha}e^{-\lambda t}
%  \label{eqn:powerlaw_cutoff}
%  \end{equation}
  We determine MLEs of $\alpha$ and $\lambda$ by maximizing the likelihood function:~\cite{clauset_power-law_2009}
  \begin{equation}
    \mathcal{L}(\alpha, \lambda) = n(1 - \alpha)\ln\lambda - n\ln\Gamma(1 - \alpha, t_{min}\lambda) - \alpha\sum_{i=1}^{n}\ln t_i - \lambda\sum_{i=1}^n t_i
  \label{eqn:powerlaw_cutoff_likelihood}
  \end{equation}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{1mode_AD_hops.pdf}
  \caption{}\label{fig:1mode_AD_hops}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{1mode_AD_dwells.pdf}
  \caption{}\label{fig:1mode_AD_dwells}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{hurst_barchart.pdf}
  \caption{}\label{fig:hurst_barchart}
  \end{subfigure}
  \caption{The parameters of the 1 mode model reveal differences in solute dynamics.
  (a) We parameterized Gaussian, $\mathcal{N}(\sigma)$, and L\'evy stable, 
  $L(\sigma, \alpha_h)$, distributions to describe solute hop lengths. We assume the 
  mean ($\mu$) to be zero for these distributions and there to be no skewness ($\beta = 0$)
  in the L\'evy stable disributions. High values of $\sigma$ and lower values of $\alpha_h$
  result in larger hops. (b) We parameterized a pure power law, $P(\alpha)$, and a 
  truncated power law, $P_T(\alpha, \lambda)$, distribution to describe solute dwell
  times. Lower values of $\alpha$ lead to heavier power law tails and higher values of 
  $\lambda$ truncate the distibution at lower dwell times. (c) Finally, we parameterized the
  hop autocorrelation function, $\gamma(H)$, to describe the degree of correlation between
  hops. Higher values of $H$ display closer to Brownian behavior.}\label{fig:1mode_parameters}
  \end{figure}

  \begin{figure}
  \centering
  \begin{subfigure}{0.475\textwidth}
  \includegraphics[width=\textwidth]{2mode_AD_hops.pdf}
  \caption{}\label{fig:2mode_AD_hops}
  \end{subfigure}
  \begin{subfigure}{0.475\textwidth}
  \includegraphics[width=\textwidth]{2mode_AD_dwells.pdf}
  \caption{}\label{fig:2mode_AD_dwells}
  \end{subfigure}
  \caption{
  %MRS6: shouldnt the values be positive below the axis as well (if that can be done) I guess they are for b, but not for A.
  %BJC6: yes, oversight, thanks.
  The two mode model parameterizes solute behavior in the pore and tails separately.
  We consider solutes to be within the pore region if they are 0.75 nm from a given pore
  center, otherwise they are in the tails. (a) Generally, movement is much more restricted
  in the tail region shown by lower $\sigma$ values (smaller hops) for the normal and L\'evy stable 
  distributions. Values of $\alpha$ are significantly lower for urea and acetic acid meaning 
  there is a larger probability that they will take large hops. (b) Dwell times are longer in 
  the tails. Lower values of $\alpha$ correspond to power laws with heavier tails and 
  thus higher probabilities of long dwell times. There is no easily discernable trend in
  $\lambda$ of the truncated power law distribution. Note that we used the same Hurst parameter
  for both modes (shown in Figure~\ref{fig:hurst_barchart}) due to a low number of 
  sufficiently long sequences of hops in each mode.}
  \label{fig:2mode_parameters}
  \end{figure}

@@

  The model parameters for the 1 and 2 mode models tell stories about each solute's
  behavior that help explain the difference between the MSDs of different solutes. 
  %BJC6: need to double check this after alpha_h c parameter simulations are re-done
  Higher values of $\sigma$ and lower values of $\alpha_h$ indicate larger average 
  hop length magnitudes by increasing the hop length distribution's width and tail 
  density respectively. Higher values of $\alpha$ indicate a lower probability of 
  long dwell times. Higher values of $\lambda$ truncate the power law distribution 
  earlier preventing extremely long dwell times. Values of $H$ closer to the Brownian
  limit of 0.5 indicate a lower degree of negative correlation between hops. All 
  of these model parameters contribute to 
  %MRS6: increase in the MSD compared to what, be specific?
  %BJC6: made more specific
  an overall increase in the predicted MSD and can be correlated to physical behavior 
  that explains differences in the MD MSDs.

  Turning first to the parameters of the 1 mode model, we can begin to break down the
  trends in solute MSDs. The parameters belonging to ethylene glycol and methanol are
  relatively similar which is consistent with their similar MD MSDs. Methanol 
  tends to stay trapped for less time and takes larger hops but the most substantial
  difference is with respect to their Hurst parameters. In fact, methanol has the lowest
  $H$ of all the solutes studied. It is possible that we have underestimated $H$ since 
  it appears that our model under-predicts the methanol MSD curve relative
  to other solutes. However, it remains plausible that methanol does have a low $H$ 
  value because it spends the majority of its time outside the pore region where collisions
  with tails are frequent. Urea has the third highest MSD which is primarily a consequence of
  more frequent and longer dwell times, indicated by lower values of $\alpha$ and 
  $\lambda$. Urea's hop lengths ($\sigma$) and correlation ($H$) are comparable to ethylene
  glycol and methanol. Acetic acid has the smallest MSD among the solutes studied due 
  to longer periods of entrapment and shorter hops. Its trapping behavior is parameterized
  by an $\alpha$ value significantly lower than other solutes, but an intermediate 
  $\lambda$ value, suggesting it experiences many medium length periods of entrapment. 
  Its hops are smaller but are slightly compensated by a heavier tailed distribution 
  (lower $\alpha_h$) than the other solutes.

  We can use the 2 mode model to gain an even deeper understanding of solute behavior
  in the pore versus in the tails. It is clear that solutes are significantly slowed 
  while they are in the tail region where long dwell times are more probable
  (smaller $\alpha$) and hops are smaller (smaller $\sigma$). Each solute spends 
  a different amount of time in the tails (see Figure~\ref{fig:AD_mode_occupation}). 
  Urea and acetic acid spend slightly more than half of their time in the tails 
  (56\% and 62\% of their time respectively) while ethylene glycol spends about 
  44\% of its time in the tails. Urea and acetic acid's compact and flat structure 
  allows it to more easily partition into the tails while ethylene glycol prefers
  the pore region due to its two hydrophilic hydroxyl groups. Meanwhile methanol 
  spends 91\% of its time in the tails likely due to its small size.  
  The value of $\alpha_h$ for urea and acetic acid in the tails is 1.50, meaning its hop distribution
  is heavy tailed relative to ethylene glycol and methanol whose $\alpha_h$ values are
  more consistent with a Gaussian distribution ($\alpha$=2). Acetic acid and urea are
  structurally similar molecules, both planar with two heavy atoms attached to a 
  carbonyl group. Their small size and rigid shape may allow them to occasionally slip
  through gaps in the tails. Meanwhile, methanol is small enough that it does not need
  to make larger jumps to escape traps.

@@

%  The parameters of the 1 mode model indicate some diversity in solute behavior. The value
%  of $\alpha$ for pure and truncated power law fits to the dwell time distributions of 
%  urea, ethylene glycol and methanol are similar. The value of $\alpha$ for acetic
%  acid is significantly lower than the rest of the solutes meaning it stays trapped 
%  for long periods of time more frequently. The value of $\lambda$ is largest for
%  methanol indicating that its longest dwell time is shorter than the longest dwell
%  times of all other solutes. When hops are fit to a Gaussian, it is clear that acetic
%  acid takes the smallest hops while methanol takes the largest. If we fit hops to a
%  L\'{e}vy stable distribution, we observe a similar trend in $\sigma$ values, but 
%  with varying weights on the distribution's tails. Acetic acid has the heaviest
%  tails (lowest $\alpha_h$), meaning it is more likely to take large hops, while 
%  ethylene glycol stays close to a Gaussian distribution (i.e. $\alpha_h$ near 2).
%  The Hurst parameters indicate a moderate degree of anti-correlation between hops. 
%  Surprisingly, methanol takes the most anti-correlated hops (lowest $H$). This is
%  likely because methanol spends the largest fraction of its time within the pores. 
%  It can still make large hops thanks to its small size, but tends to bounce around
%  the tails.

%  BJC4: urea and ethylene glycol only
%  The parameters of the 1 mode model are similar between urea and ethylene glycol which 
%  is not surprising considering their similar MD MSDs. Dwell times by 
%  ethylene glycol are shorter as shown by its larger $\alpha$ and $\lambda$ values. Both
%  solutes make similarly sized hops with hop distributions that are relatively close 
%  to Gaussian (i.e. $\alpha_h$ near 2) when fit to a L\'evy stable distribution. Finally,
%  both solutes exhibit a similar degree of correlation between hops with ethylene glycol
%  exhibiting motion closer to Brownian.

%  The difference in parameters of each mode of the 2 mode sFBM model offer additional
%  mechanistic insight which the 1 mode model lacks. It is clear that solutes are 
%  significantly slowed while they are in the tail region (mode 2) where long dwell times
%  are more probable and hops are smaller (smaller $\alpha$). 
% BJC: I'm not sure how valid it is to analyze lambda because it is dependent on alpha. There is some counterbalancing going on.  
% The values of $\lambda$, however, do not 
% appear to be directly correlated to mode. For example, $\lambda$ for ethylene glycol is
% lower in the pores, meaning its longest dwell times in the pores are longer than its
% longest dwell times in the tails. This may be a consequence of    
%  Interestingly, $\alpha_h$ for urea and acetic acid in mode 2 is 1.50 meaning its 
%  hop distribution is heavy tailed relative to ethylene glycol and methanol whose 
%  $\alpha_h$ values are more consistent with a Gaussian distribution. Acetic acid and
%  urea are structurally similar molecules, both planar with two heavy atoms attached to
%  a carbonyl group. Their small size and rigid shape may allow them to slip through 
%  gaps in the tails. Meanwhile, methanol is small enough that it does not need to make 
%  larger jumps to escape traps.

%  BJC4: Urea and ethlyene glycol only
%  The parameters of the 2 mode model are again similar between urea and ethylene glycol, 
%  but the difference between parameters of each mode offer more detailed mechanistic
%  insight than the 1 mode model. It is clear that solutes are significantly slowed while
%  they are in the tail region where long dwell times are more probable (lower $\alpha$)
%  and hops are smaller (smaller $\sigma$).  
%  Interestingly, $\alpha_h$ for urea in mode 2 is 1.50 meaning its hop distribution is
%  heavy tailed relative to ethylene glycol which has an $\alpha$ more consistent 
%  with a Gaussian distribution. Although urea's $\sigma$ parameter is much smaller in 
%  the tails, it still has an appreciable probability of making large hops. This could 
%  be a consequence of urea's relatively small size and rigid shape compared to ethylene glycol.
  %Ethylene glycol is a linear chain that can
  %easily become entangled among the alkane tails while urea is planar with its four
  %heavy atoms bonded to a single central atom.

@@

  To understand the behavior of the MSDDM, we studied the $\beta$ parameter derived 
  from variations on each model, visualized in Figure~\ref{fig:beta_parameters}. First, 
  we removed anti-correlation between hops in the sFBMcut trajectory (set $H$=0.5). 
  The $\beta$ parameter drops to values similar to the MSDDM. When we remove anti-correlation
  \textit{and} dwell times between hops (set dwell times equal to 1), effectively simulating 
  Brownian motion, we observe similar $\beta$ parameters. These two variations imply that,
  in the AD models, the $\beta$ parameter is only a function of $H$ and not dependent on
  dwell times ($\alpha$, $\lambda$) or hop lengths ($\sigma$). The MSDDM is fundamentally similar to 
  the AD model in that one makes correlated draws from a hop distribution. Therefore,
  we should expect the $\beta$ value of the MSDDM to be larger than that of Brownian 
  motion.
  %Although the dwell times are
  %insignificant compared to the AD model (compare Figures~\ref{fig:ad_eyetest} and
  %\ref{fig:msddm_eyetest} for example), we have just shown
